AHABus \& FCORE:\\Modular Bus for High-Altitude Balloon Missions

### 2017-04-10 chapters/03-methodology.tex
Finish methodology

The configuration tool was written in ruby because it allows easy parsing of
JSON files. An example output source file is shown in figure \ref{fig:conf-out},
generated from the example configuration file discussed previously.

\begin{lstlisting}[
    caption=FCORE - Example Configuration Output,
    label=lst:conf-out
]
// FCORE Configuration File - FCORE Test 1
// Generated on 2017-03-29 by fcore_config.rb

@@

\subsection{Packet Parser}

@@

@@

@@

>>>>

The configuration tool was written in ruby because it allows easy parsing of
JSON files. An example output source file is shown in listing 
\ref{lst:conf-out}, generated from the example configuration file discussed
previously.

\begin{lstlisting}[
    caption=FCORE - Example Configuration Output,
    label=lst:conf-out,
    language=c
]
// FCORE Configuration File - FCORE Test 1
// Generated on 2017-03-29 by fcore_config.rb

@@

The ground segment was based on Dl-Fldigi, an open-source binary radio decoder.
While Dl-Fldigi can decode RTTY signals, it was meant to decode RTTY text and
not binary data like the \acrshort{ahabus} packet radio protocol requires.
The data decoded by the software is not written to any file, but instead printed
in the main window, which means that byte which values are outside the range of
ASCII printable characters were invisible.

In order to allow a decoding tool to work on the full binary stream, a fork of
Dl-Fldigi was modified so that the binary stream could be extracted. When the
modified version starts, it creates a local network socket, to which any
byte decoded from RTTY streams are forwarded. This design was chosen because
most programming languages provide support for network communications, which
means that tools could easily be written to work with AHABus frame streams, such
as the packet parser discussed in the following section.

\subsection{Packet Parser}
\label{sec:packet-dispatcher}

For the purpose of debugging, a simple command-line based packet parser and
monitor was built upon the decoder discussed in section
\ref{sssec:rtx-decoder}. Because the platform was still at the prototype stage,
it was kept fairly simple. The location metadata contained in the packets is
displayed directly, as are system health packets. The data contained in packets
coming from payloads is written directly to one file for each payload. Listing
\ref{lst:fcore-parser-out} shows an example output from the packet parser.

\begin{lstlisting}[
    caption=Ground Segment - Example Packet Parser Output,
    label=lst:fcore-parser-out
]
[1490711516]: frame start detected
[1490711531]: decoded valid payload packet (0x14)
[1490711531]: 	>>>> FIX(56.462000deg, -2.970700deg, 5579m)
[1490711531]: rx stats: 7569 received, 7424/0 frame bytes (0 fixed)
[1490711545]: frame start detected
[1490711559]: decoded valid system packet
[1490711559]: 	>>>> FIX(56.462000deg, -2.970700deg, 5747m)
[1490711559]: 	>>>> FCORE//SYS_HEALTH :: G/U,P0A/U,P14/U
[1490711559]: rx stats: 7830 received, 7680/0 frame bytes (0 fixed)
[1490711569]: frame start detected
\end{lstlisting}

For testing purposes, the parser was also set to output statistics on the amount
of data received, fixed errors and number of frames decoded or lost.

@@

Evaluation and testing of the project proved difficult because of the nature
of the prototype: embedded systems provide little, if any way to debug and
observe code behaviour. Instead, most of the testing had to focus on the data
received by the ground segment. Nonetheless, testing was conducted through
two main methods discussed in this section.

For all tests, the experimental setup was kept consistent: an ESP8266
development board was used as the \acrshort{obc}, while two Arduino Uno boards
were connected as payloads, generating fake instrument data. A \SI{5}{\volt}
power supply was connected to the power lines.

@@

The day-in-the-life test was meant to simulate a full \acrshort{hab} mission,
in order to evaluate both the overall viability of the platform, and test the
performance of the \acrshort{ahabus} platform's subsystems.

In order to come as close as possible to real-life conditions, the
\acrshort{gnss} receiver was replaced with an Arduino board programmed to
simulate the position updates of a receiver attached to a \acrlong{hab}
throughout ascent and descent.

Because the test was executed locally, the long-range aspect of the radio
communications could only be simulated by using a short antenna on the reception
side, and no antenna on the simulated platform.

@@

The goal of the resilience tests was to test the performance of the packet radio
protocol, and specifically the \acrlong{fec}/Frame layer. To simulate a noisy
radio channel, a modified version of \acrshort{fcore} was built so that it
would randomly change the value of a byte before transmitting it. Knowing the
maximum theoretical correction limit of the \acrshort{fec} algorithm
($\frac{16}{256}$), three average error rates
($\frac{corrupted}{transmitted}$) were tested:

\begin{itemize}
    \item well under the limit ($\frac{8}{256}$);
    \item just under the limit ($\frac{14}{256}$);
    \item above the limit ($\frac{18}{256}$).
\end{itemize}
